{\pkg}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2019-02-02 papers/lang2018/ms.tex
Updated links

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pippkg}{\todo{\tt yggdrasil-framework}}
\newcommand{\condapkg}{\todo{\tt yggdrasil}}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{\todo{cis\_interface}}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt yggrun}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/yggdrasil}{\todo{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/yggdrasil/}{\todo{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/yggdrasil/hackathon2018/index.html}{\todo{#1}}}

@@

The next step in each model wrapper is to receive the static input variables (those that are not being looped over). This step occurs on lines 19-33 in the root model wrapper (Listing \ref{lst:wrap:root}) and lines 15-34 in the shoot model wrapper (Listing \ref{lst:wrap:shoot}). Next, each model wrapper sends the initial mass to the output so that the output will contain the entire mass history. This occurs on lines 58-63 in the root model wrapper and lines 36-39 in the shoot model wrapper. The majority of these lines are devoted to error handling and print statements. The syntax for sending/receiving messages differs slightly from language to language, but each will return a flag indicating if the send/receive was successful or not. If an input channel is still open, a receive call will block until the channel is closed or a message is received. If the input channel is closed (either because of an error or because it was closed by the source), the flag will indicate this and the received message should not be used. If an output channel is open, a send call will return immediately while a worker thread handles asynchronous completion of the send request. If an output channel is closed, a send call will return immediately with a flag indicating failure. Additional information about the interface calls for sending and receiving can be found in the ``Model Interface" section of the documentation\footnote{{\tt \todo{link}}}.

>>>>

%---------------------------------------------------------------------------------
% CONTROL THINGS
\newcommand{\todo}[1]{{\color{red}{#1}}}
\newcommand{\addref}{{\color{red}(ref. needed)}}
\newcommand{\Msol}{\,M$_{\odot}$}
\newcommand{\TB}{\,Tbytes}
\newcommand{\pippkg}{{\tt yggdrasil-framework}}
\newcommand{\condapkg}{{\tt yggdrasil}}
\newcommand{\pkg}{{\tt yggdrasil}{}}
\newcommand{\cis}{{\tt cis\_interface}{}}
\newcommand{\pkglink}{yggdrasil}
%\newcommand{\pkg}{{\tt \todo{cis\_interface}}{}}
\newcommand{\pkgrun}{{\tt yggrun}}
\newcommand{\A}{Appendix{ }}
\newcommand{\hrefgit}[1]{\href{https://github.com/cropsinsilico/yggdrasil}{{#1}}}
\newcommand{\hrefdoc}[1]{\href{https://cropsinsilico.github.io/yggdrasil/}{{#1}}}
\newcommand{\hrefhack}[1]{\href{https://cropsinsilico.github.io/yggdrasil/hackathon2018/index.html}{{#1}}}

@@

The next step in each model wrapper is to receive the static input variables (those that are not being looped over). This step occurs on lines 19-33 in the root model wrapper (Listing \ref{lst:wrap:root}) and lines 15-34 in the shoot model wrapper (Listing \ref{lst:wrap:shoot}). Next, each model wrapper sends the initial mass to the output so that the output will contain the entire mass history. This occurs on lines 58-63 in the root model wrapper and lines 36-39 in the shoot model wrapper. The majority of these lines are devoted to error handling and print statements. The syntax for sending/receiving messages differs slightly from language to language, but each will return a flag indicating if the send/receive was successful or not. If an input channel is still open, a receive call will block until the channel is closed or a message is received. If the input channel is closed (either because of an error or because it was closed by the source), the flag will indicate this and the received message should not be used. If an output channel is open, a send call will return immediately while a worker thread handles asynchronous completion of the send request. If an output channel is closed, a send call will return immediately with a flag indicating failure. Additional information about the interface calls for sending and receiving can be found in the ``Model Interface" section of the documentation\footnote{{\tt https://cropsinsilico.github.io/\pkglink/model\_interface.html}}.
